---
title: "data regression analysis"
output: html_notebook
---

Constants

```{r}
PEARSON_FILE <- "../all/pearson_corr/corr_mcrae_wikigiga.txt"
FILE <- "../all/hier_clust/wordnet_match_wikigiga.txt"
```


```{r}
pearson <- read.table(PEARSON_FILE, sep="\t", header=TRUE)
data <- read.table(FILE, sep="\t", header=TRUE, na.strings=c("n/a"))
```

Merge feature data from Pearson file with a particular WordNet match column.

```{r}
colnames(pearson)
colnames(data)
```

```{r}
new_data <- pearson
new_data["wordnet_corr"] <- data[,c("dendrogram..0.8..wordnet..7")]
new_data[is.na(new_data)] <- 0.0
new_data["wordnet_corr"] <- scale(new_data["wordnet_corr"])
```

Baseline regression: use frequency, etc. lexical features, but leave out taxonomy features.

```{r}
colnames(new_data)
```

```{r}
attach(new_data)
baseline_lm <- lm(wordnet_corr ~ log.BNC_freq. + num_feats_tax + familiarity + tot_num_feats + polysemy)
summary(baseline_lm)
```


Full model, including domain features

```{r}
cn <- colnames(new_data)
full_formula <- as.formula(paste("wordnet_corr", "~", paste(cn[c(3:70)], collapse="+")))
full_formula
full_lm <- lm(full_formula, data=new_data)
summary(full_lm)
```

## Comparing models

```{r}
anova(full_lm)
```


```{r}
anova(baseline_lm, full_lm)
```

## Comparing with the pearson model

Let's compute the Pearson LM here and compare its weights with the weights from the WordNet LM.

```{r}
cn <- colnames(new_data)
new_data["correlation"] <- scale(new_data["correlation"])
pearson_formula <- as.formula(paste("correlation", "~", paste(cn[c(3:70)], collapse="+")))
pearson_formula
pearson_lm <- lm(pearson_formula, data=new_data)
summary(pearson_lm)
```

Fetch the coefficients, and slice off the baseline features:

```{r}
names(coef(pearson_lm))
names(coef(pearson_lm))[-(1:6)]
coefs <- cbind(pearson=coef(pearson_lm)[-(1:6)],
               wordnet=coef(full_lm)[-(1:6)])
```

```{r}
plot(coefs)
```

Correlation:

```{r}
cor(coefs)
```

Rank correlation:

```{r}
coef_ranks <- apply(coefs, 2, rank)
coef_ranks
```

```{r}
plot(coef_ranks)
```



```{r}
cor(coefs, method="spearman")
```

